### 2023-11-17 paper.tex
initial commit of the latex template, ICLR 2024 version

\documentclass{article} % For LaTeX2e
\usepackage{iclr2024_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}

\title{InformatiCup 2024 Ctrl-Alt-Defeat}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Max Buchholz, Lukas Müller, Levi Otterbach \& Raphael Weber}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\subsubsection*{Acknowledgments}

\bibliography{bibliography}
\bibliographystyle{iclr2024_conference}

\appendix
\section{Appendix}
You may include other additional sections here.

\end{document}

### 2023-12-02 paper.tex
displayed names
added the structure of our paper
Updated the structure
Draft for introduction

@@
 
-%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
+\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
 \begin{document}
@@
 \end{abstract}
+
+\section{Introdution}
+The development of generative Machine Learning models made huge steps forward, when it comes to comparison with human crafted artefacts.
+Large Language Models enable the generation of texts in all kind of different flavours and styles.
+Image generating models like ViT models can generate images, that already was used create fake images, that were reported as true by media.
+Other news showed artists winning art competitions with generated art.
+So there is an interest to detect, which texts or images are generated and which ones are real pictures or human-written text.
+
+So researchers evaluated different approaches to detect fake images and texts.
+But from other computer vision tasks like object detection, adversarial attacks are known, that can reduce the performance by artificially manipulating real images to reduce the performance of e.g.
+visual object detection models.
+This raises the questions, whether and how it is possible to manipulate generated artifacts (e.g.
+images and texts) to reduce the accuracy of detectors.
+
+It is necessary to evaluate whether such techniques exist, because otherwise one could rely on detectors, which can easily be tricked.
+If easy efficient manipulation techniques exist, better detectors need to be developed that are robust against these techniques.
+Also one might be able to improve the robustness and accuracy of existing detectors, when one understands how the attacks can be crafted.
+
+Therefore we came up with the following research questions:
+
+RQ1: How can generated images be manipulated to trick fake image detectors?
+
+RQ2: How can generated texts be manipulated to trick fake text generators?
+
+The report is structured as followed: After this introduction chapter 2 presents related work, especially text and image generating models as well  fake image and fake text detectors.
+Chapter 3 presents the methodology of our work.
+Chapter 4 presents the results our experiments.
+Chapter 5 discusses the results and chapter 6 will conclude the work.
+
+\section{Related work}
+
+\subsection{Generating models}
+
+\subsubsection{Image generating models}
+
+\subsubsection{Text generating models}
+
+\subsection{Detector models}
+
+\subsubsection{Image detector models}
+
+\subsubsection{Text detector models}
+
+\section{Method}
+
+\section{Results}
+
+\section{Discussion}
+
+\section{Conclusion}
 

### 2023-12-02 paper.tex
Initial draft of the method section

--- 2023-11-17 paper.tex
@@
 \end{abstract}
+
+\section{Introdution}
+
+\section{Related work}
+
+\subsection{Generating models}
+
+\subsubsection{Image generating models}
+
+\subsubsection{Text generating models}
+
+\subsection{Detector models}
+
+\subsubsection{Image detector models}
+
+\subsubsection{Text detector models}
+
+\section{Method}
+To test and evaluate the effect of different data augmentation techniques on the detection capabilities of fake image or text detectors, we created a pipeline of three components: The first component is a generator, which is a model that is capable of generating fake images or text.
+The second component is a processor.
+After inputting a generated image or text, this component augments the data with a specified method.
+The third component contains a detector, which returns whether an input is a fake artefact or a real one.
+This way we can compare it to the ground truth, to evaluate the capabilities of the detector.
+By comparing the results with augmented artefacts and with the genrated artefacts without augmentation, we can see how effective different techniques are to trick ai detectors.
+
+\section{Results}
+
+\section{Discussion}
+
+\section{Conclusion}
 

### 2023-12-02 paper.tex
Section abou the RoBERTa Base OpenAI detector

--- 2023-11-17 paper.tex
@@
 \end{abstract}
+
+\section{Introdution}
+
+\section{Related work}
+
+\subsection{Generating models}
+
+\subsubsection{Image generating models}
+
+\subsubsection{Text generating models}
+
+\subsection{Detector models}
+
+\subsubsection{Image detector models}
+
+\subsubsection{Text detector models}
+
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
+It was obtained by fine-tune a RoBERTa base model with the ouputs of the GPT-2 model containing 1,5 Billion parameters.
+RoBERTa Base OpenAI Detector can be used to classify text, on whether it is likely to be created by the GPT-2 model.
+It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+
+\section{Method}
+
+\section{Results}
+
+\section{Discussion}
+
+\section{Conclusion}
 

### 2023-12-04 paper.tex
Fix minor issues
typos, rephrasing, etc.

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
-It was obtained by fine-tune a RoBERTa base model with the ouputs of the GPT-2 model containing 1,5 Billion parameters.
-RoBERTa Base OpenAI Detector can be used to classify text, on whether it is likely to be created by the GPT-2 model.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
+The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
 It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.

### 2023-12-04 paper.tex
Incoorporate rephrasing

--- 2023-12-02 paper.tex
@@
 
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
-It was obtained by fine-tune a RoBERTa base model with the ouputs of the GPT-2 model containing 1,5 Billion parameters.
-RoBERTa Base OpenAI Detector can be used to classify text, on whether it is likely to be created by the GPT-2 model.
-It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
-
 \section{Method}
+To test and evaluate the effect of different data augmentation techniques on the detection capabilities of fake image or text detectors, we created a pipeline of three components: The first component is a generator, which is a model capable of generating fake images or texts.
+The second component is a processor which augments the data through a specified method, after inputting a generated image or text.
+The last component is a detector, which suggests an input being either real or fake.
+This way we can compare it to the ground truth, to evaluate the capabilities of the detector.
+By comparing the results with augmented artefacts and with the generated ones without augmentation, we can evaluate the effectiveness of different AI detector-tricking techniques.
 

### 2023-12-04 paper.tex
Implement rephrasing and suggestions

--- 2023-12-02 paper.tex
@@
 
-\section{Introdution}
+\section{Introduction}
+The development of generative Machine Learning models make huge steps forward in the last years considering comparison with human crafted artefacts.
+Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles.
+There were already scenarios were fake images, created by image-generation models such as Vision Transformer (ViT) models, were reported as real ones by media.
+Other news showed artists winning art competitions with generated art.
+That means that there is an interest in detecting, which texts or images are generated and which ones are real pictures or human-written texts.
+
+Therefore researchers evaluated different approaches to detect fake images and texts.
+But these attempts are from other computer vision tasks like object detection, adversarial attacks are known, that can reduce the performance by artificially manipulating real images to reduce the performance of e.g.
+visual object detection models.
+This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g.
+images and texts) to reduce the accuracy of detectors.
+
+It is necessary to evaluate whether or not such techniques exist.
+If not one could rely on detectors, which can easily be easily tricked.
+If there are techniques exist that allow easy and efficient manipulation, better detectors, which are robust against those, need to be developed.
+Another solution would be to improve the robustness and accuracy of existing detectors, when understanding how the attacks can be crafted.
+
+Therefore we came up with the following research questions:
+
+RQ1: How can generated images be manipulated to trick fake image detectors?
+
+RQ2: How can generated texts be manipulated to trick fake text generators?
+
+The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generating models as well as fake image and fake text detectors.
+Chapter 3 presents the methodology of our work, followed by chapter 4 which shows the results of our experiments.
+Afterwards in  Chapter 5 those results will be discussed and our work will be concluded in chapter 6.
 
@@
 \subsubsection{Text detector models}
-
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
-It was obtained by fine-tune a RoBERTa base model with the ouputs of the GPT-2 model containing 1,5 Billion parameters.
-RoBERTa Base OpenAI Detector can be used to classify text, on whether it is likely to be created by the GPT-2 model.
-It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
 

### 2023-12-04 paper.tex
Typo
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>

--- 2023-12-04 paper.tex
@@
 
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
+The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
+It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+
 \section{Method}
 To test and evaluate the effect of different data augmentation techniques on the detection capabilities of fake image or text detectors, we created a pipeline of three components: The first component is a generator, which is a model capable of generating fake images or texts.
-The second component is a processor which augments the data through a specified method, after inputting a generated image or text.
+The second component is a processor which augments the data through a specified method, after given a generated image or text.
 The last component is a detector, which suggests an input being either real or fake.

### 2023-12-04 paper.tex
Apply rephrasing suggestions from code review
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2023-12-04 paper.tex
@@
 
-\section{Introdution}
+\section{Introduction}
+The development of generative Machine Learning models made huge steps forward in the last years, considering the comparison with human crafted artefacts.
+Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles.
+Image generating models like Vision Transformer (ViT) models already created fake images being reported as real by media.
+Other news showed artists winning art competitions with generated art.
+This creates an interest in detecting which texts or images are AI generated and which ones are real images or human-written texts.
+
+Therefore researchers evaluated different approaches to detect fake images and texts.
+Fortunately some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e.
+g.
+visual object detection, by artificially manipulating real images.
+This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g.
+images and texts) to reduce the accuracy of detectors.
+
+It is necessary to evaluate whether such techniques exist, because otherwise one could rely on detectors, which can easily be tricked.
+If easy efficient manipulation techniques exist, existing detectors need to be improved or better detectors need to be developed that are robust against these techniques.
+But this preconditions a good understanding of the way attacks are performed.
+
+Therefore we came up with the following research questions:
+
+RQ1: How can generated images be manipulated to trick fake image detectors?
+
+RQ2: How can generated texts be manipulated to trick fake text generators?
+
+The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generating models as well as fake image and text detectors.
+Chapter 3 presents the methodology of our work followed by chapter 4 presenting the results of our experiments.
+Afterwards the results will be discussed in chapter 5 and chapter 6 will conclude the work.
 
@@
 \section{Method}
-To test and evaluate the effect of different data augmentation techniques on the detection capabilities of fake image or text detectors, we created a pipeline of three components: The first component is a generator, which is a model capable of generating fake images or texts.
-The second component is a processor which augments the data through a specified method, after inputting a generated image or text.
-The last component is a detector, which suggests an input being either real or fake.
-This way we can compare it to the ground truth, to evaluate the capabilities of the detector.
-By comparing the results with augmented artefacts and with the generated ones without augmentation, we can evaluate the effectiveness of different AI detector-tricking techniques.
 

### 2023-12-05 paper.tex
Include suggested rephrasings

@@
 Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles.
-Image generating models like Vision Transformer (ViT) models already created fake images being reported as real by media.
+Image generating models like Vision Transformer (ViT) already created fake images being reported as real by media.
 Other news showed artists winning art competitions with generated art.
@@
 Therefore researchers evaluated different approaches to detect fake images and texts.
-Fortunately some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e.
+Some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e.
 g.
@@
 It is necessary to evaluate whether such techniques exist, because otherwise one could rely on detectors, which can easily be tricked.
-If easy efficient manipulation techniques exist, existing detectors need to be improved or better detectors need to be developed that are robust against these techniques.
-But this preconditions a good understanding of the way attacks are performed.
+If easy efficient manipulation techniques exist, detectors need to be improved or better detectors need to be developed that are robust against these techniques.
+But this requires a good understanding how the attacks are performed.
 
@@
 Chapter 3 presents the methodology of our work followed by chapter 4 presenting the results of our experiments.
-Afterwards the results will be discussed in chapter 5 and chapter 6 will conclude the work.
+Afterwards the results will be discussed in chapter 5 and chapter 6 will conclude this paper.
 

### 2023-12-05 paper.tex
Draft for introduction (#8)
* Draft for introduction

* Implement rephrasing and suggestions

* Apply rephrasing suggestions from code review

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

* Include suggested rephrasings

---------

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
+The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
+It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+
 \section{Method}
+To test and evaluate the effect of different data augmentation techniques on the detection capabilities of fake image or text detectors, we created a pipeline of three components: The first component is a generator, which is a model capable of generating fake images or texts.
+The second component is a processor which augments the data through a specified method, after given a generated image or text.
+The last component is a detector, which suggests an input being either real or fake.
+This way we can compare it to the ground truth, to evaluate the capabilities of the detector.
+By comparing the results with augmented artefacts and with the generated ones without augmentation, we can evaluate the effectiveness of different AI detector-tricking techniques.
 

### 2023-12-19 paper.tex
First report and references for Stable diffusion

@@
 \subsubsection{Image generating models}
+The first image generating model we us is the Stable Diffusion model.
+It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
 

### 2023-12-28 paper.tex
add RADAR section
citation does not work

--- 2023-12-05 paper.tex
@@
 
+The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
+In the training stage the detector tryed to differentiate between human and ai text while a paraphraser trained to make the text more humanly.
+The Ai-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{RADAR}.
+
 \section{Method}

### 2023-12-28 paper.tex
add initial text

--- 2023-12-05 paper.tex
@@
 
+The \textbf{ai-image-det-resnet18} model is a community made, fine tuned, resnet18 based, pretrained image detection model.
+For finetuneing the author kgmann on Hugging Face used the AI or Not dataset.
+ResNet-18 is a convolutional neural network that is 18 layers deep.
+It got pretrained by over a million images from the ImageNet database.
+\cite{https://arxiv.org/pdf/1512.03385.pdf}
+
 \subsubsection{Text detector models}

### 2023-12-28 paper.tex
add text

--- 2023-12-19 paper.tex
@@
 \subsubsection{Image generating models}
-The first image generating model we us is the Stable Diffusion model.
-It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
 
@@
 \subsubsection{Image detector models}
+
+The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset.
+swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{https://arxiv.org/pdf/2103.14030.pdf}.
 

### 2023-12-29 paper.tex
fixed citation
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2023-12-28 paper.tex
@@
 The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
-In the training stage the detector tryed to differentiate between human and ai text while a paraphraser trained to make the text more humanly.
-The Ai-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{RADAR}.
+In the training stage the detector tryed to differentiate between human and AI text while a paraphraser trained to make the text more human.
+The Ai-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
 

### 2023-12-29 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>
Update paper.tex
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>
Fix citation
add short text

--- 2023-12-28 paper.tex
@@
 
+\textbf{Winston AI} is a commertial AI text detector that starts at 18\$ a month.
+The two primary methods for checking if a text is AI written is firstly Linguistic analysis.
+Linguistic analysis analyses every text of its characteristics like repetitivness.
+These characteristics are different between AI and humans.
+The other is Data Training, where the detector saw many AI written texts of one model and learned unice characteristics that this model uses which than can be detected.\cite{Winston AI}
+
 \subsubsection{Text generating models}
@@
 \subsubsection{Image detector models}
-
-The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset.
-swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{https://arxiv.org/pdf/2103.14030.pdf}.
 

### 2023-12-29 paper.tex

--- 2023-12-29 paper.tex
@@
 The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
-In the training stage the detector tryed to differentiate between human and AI text while a paraphraser trained to make the text more human.
-The Ai-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
+In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
+The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
 

### 2023-12-29 paper.tex
Update paper.tex

@@
 
+The \textbf{ai-image-det-resnet18} model is a community made, fine tuned, resnet18 based, pretrained image detection model.
+For fine tuning the author kgmann on Hugging Face used the AI or Not dataset.
+ResNet-18 is a convolutional neural network that is 18 layers deep.
+It got pretrained by over a million images from the ImageNet database.
+\cite{he2015deep}
+
 \subsubsection{Text detector models}
@@
 It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
-
-The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
-In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
-The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
 

### 2023-12-29 paper.tex
Update paper.tex

@@
 
-The \textbf{ai-image-det-resnet18} model is a community made, fine tuned, resnet18 based, pretrained image detection model.
-For fine tuning the author kgmann on Hugging Face used the AI or Not dataset.
+The \textbf{ai-image-det-resnet18} model is a community made, fine-tuned, resnet18 based, pretrained image detection model.
+For fine-tuning the author kgmann on Hugging Face used the AI or Not dataset.
 ResNet-18 is a convolutional neural network that is 18 layers deep.

### 2023-12-29 paper.tex

--- 2023-12-29 paper.tex
@@
 
+The \textbf{ai-image-det-resnet18} model is a community made, fine-tuned, resnet18 based, pretrained image detection model.
+For fine-tuning the author kgmann on Hugging Face used the AI or Not dataset.
+ResNet-18 is a convolutional neural network that is 18 layers deep.
+It got pretrained by over a million images from the ImageNet database.
+\cite{he2015deep}
+
 \subsubsection{Text detector models}

### 2023-12-29 paper.tex
add citation

--- 2023-12-29 paper.tex
@@
 
-The \textbf{ai-image-det-resnet18} model is a community made, fine-tuned, resnet18 based, pretrained image detection model.
-For fine-tuning the author kgmann on Hugging Face used the AI or Not dataset.
-ResNet-18 is a convolutional neural network that is 18 layers deep.
-It got pretrained by over a million images from the ImageNet database.
-\cite{he2015deep}
+The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset.
+swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{liu2021swin}.
 

### 2023-12-29 paper.tex
Fix typos and citation

@@
 
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+The two primary methods for checking if a text is AI written is firstly Linguistic analysis.
+Linguistic analysis analyses every text of its characteristics like repetitiveness.
+These characteristics are different between AI and humans.
+The other is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which than can be detected.\cite{WinstonAI}
+
 \subsubsection{Text generating models}
@@
 \subsubsection{Image detector models}
-
-The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset.
-swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{liu2021swin}.
 

### 2023-12-29 paper.tex
add max change
Update paper.tex
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

@@
 \textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-The two primary methods for checking if a text is AI written is firstly Linguistic analysis.
-Linguistic analysis analyses every text of its characteristics like repetitiveness.
+They have two primary methods for checking if a text is AI written.
+Firstly Linguistic analysis analyses every text of its characteristics like repetitiveness.
 These characteristics are different between AI and humans.
-The other is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which than can be detected.\cite{WinstonAI}
+Secondly the other is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which than can be detected.\cite{WinstonAI}
 

### 2023-12-29 paper.tex
Fix typo

--- 2023-12-29 paper.tex
@@
 
-The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset.
-swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{liu2021swin}.
+The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.
+Swin-Transformer by Microsoft is a new Vision Transformer which makes use of hierarchical windows.
+This reduces the self-attention to not-overlapping windows of other areas of the image \cite{liu2021swin}.
 

### 2023-12-29 paper.tex

@@
 It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+
+The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
+In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
+The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
 

### 2023-12-29 paper.tex

@@
 
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
+Firstly Linguistic analysis analyses every text of its characteristics like repetitiveness.
+These characteristics are different between AI and humans.
+Secondly the other is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which than can be detected.\cite{WinstonAI}
+
 \subsubsection{Text generating models}

### 2024-01-05 paper.tex
Update paper.tex
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>
Added some of the given feedback

--- 2023-12-29 paper.tex
@@
 Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles.
-Image generating models like Vision Transformer (ViT) already created fake images being reported as real by media.
+Image generative models like Vision Transformer (ViT) already created fake images being reported as real by media.
 Other news showed artists winning art competitions with generated art.
@@
 visual object detection, by artificially manipulating real images.
+
+As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} in which the topic is to manipulate a detectable source in a way that the detector does not recognize it anymore.
 This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g.
@@
 
-The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generating models as well as fake image and text detectors.
+The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generative models as well as fake image and text detectors.
 Chapter 3 presents the methodology of our work followed by chapter 4 presenting the results of our experiments.
@@
 
-\subsection{Generating models}
+\subsection{Generative models}
 
-\subsubsection{Image generating models}
+\subsubsection{Image generative models}
 
-\subsubsection{Text generating models}
+\subsubsection{Text generative models}
 

### 2024-01-05 paper.tex
Added the image processors part

--- 2023-12-29 paper.tex
@@
 
+We used the aforementioned models for generating and detecting texts and images.
+As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise.
+Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera \cite{mohammed2016study}.
+The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}.
+\\
+There are several types of noise that can affect images.
+Some of these noise models are: Gaussian noise, White noise, Fractal noise, Salt \& Pepper noise, Periodic noise, Quantization noise, Speckle noise, Poisson noise, Poisson-Gaussian noise, Structured noise, Gamma noise and Rayleigh noise \cite{gonzalez2009digital}.
+The three common types of image noise are: Gaussian noise, Salt \& Pepper noise, and Speckle noise \cite{al2010comparative}.
+That is why we used those three, as well as the Poisson noise.
+
 \section{Results}

### 2024-01-08 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-05 paper.tex
@@
 
-As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} in which the topic is to manipulate a detectable source in a way that the detector does not recognize it anymore.
+As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} in which the topic is to manipulate a detectable source in a way that the detector does not recognize it as AI-generated anymore.
 This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g.

### 2024-01-08 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-05 paper.tex
@@
 As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise.
-Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera \cite{mohammed2016study}.
+Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera.
 The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}.

### 2024-01-08 paper.tex
deleted subsections

--- 2024-01-08 paper.tex
@@
 Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles.
-Image generative models like Vision Transformer (ViT) already created fake images being reported as real by media.
+Image generating models like Vision Transformer (ViT) already created fake images being reported as real by media.
 Other news showed artists winning art competitions with generated art.
@@
 visual object detection, by artificially manipulating real images.
-
-As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} in which the topic is to manipulate a detectable source in a way that the detector does not recognize it as AI-generated anymore.
 This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g.
@@
 
-The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generative models as well as fake image and text detectors.
+The report is structured as follows: After this introduction chapter 2 presents related work, especially text and image generating models as well as fake image and text detectors.
 Chapter 3 presents the methodology of our work followed by chapter 4 presenting the results of our experiments.
@@
 
-\subsection{Generative models}
+\subsection{Generating models}
 
-\subsubsection{Image generative models}
+\subsubsection{Image generating models}
 
-\subsubsection{Text generative models}
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
+Firstly linguistic analysis analyses every text for its characteristics like repetitiveness.
+These characteristics are different between AI and humans.
+Secondly the other is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which than can be detected.
+\cite{WinstonAI}
+
+\subsubsection{Text generating models}
 

### 2024-01-14 paper.tex

@@
 \subsubsection{Image generating models}
-
-\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-They have two primary methods for checking if a text is AI written.
-Firstly linguistic analysis analyses every text for its characteristics like repetitiveness.
-These characteristics are different between AI and humans.
-Secondly the other is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which than can be detected.
-\cite{WinstonAI}
+The first image generating model we us is the Stable Diffusion model.
+It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
 

### 2024-01-14 paper.tex
finished stable diffusion text

@@
 
+Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
+Due to its work directly in pixel space, they are very computational expensive.
+To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders.
+This works without losing quality and flexibility.
+\cite{Rombach_2022_CVPR}
+
 \subsubsection{Text generating models}

### 2024-01-14 paper.tex
Finished Dall-E section

--- 2024-01-14 paper.tex
@@
 \subsubsection{Image generating models}
-The first image generating model we us is the Stable Diffusion model.
-It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
+As a second image generative model we use Dall-E from OpenaAI (\url{https://openai.com/dall-e-3}).
+Dall-E works by modelling text and image tokens as a single data stream.
+This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+
+This is done in two steps: 
+\begin{enumerate}
+	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
+	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
+\end{enumerate}
+
+The exact procedure proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
 

### 2024-01-14 paper.tex
finished gpt section

--- 2024-01-14 paper.tex
@@
 \subsubsection{Image generating models}
-The first image generating model we us is the Stable Diffusion model.
-It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
 
 \subsubsection{Text generating models}
+We choose the GPT model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+
+Radford et. al try to avoid this problem in a simple two step procedure:
+\begin{enumerate}
+	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
+	\item Discriminative fine-tuning on every specific task.
+\end{enumerate}
+
+To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
 

### 2024-01-14 paper.tex
added feedback

@@
 
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
+Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
+One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
+So this method is more generator-specific.
+\cite{WinstonAI}
+
 \subsubsection{Text generating models}
-We choose the GPT model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
-
-Radford et. al try to avoid this problem in a simple two step procedure:
-\begin{enumerate}
-	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
-	\item Discriminative fine-tuning on every specific task.
-\end{enumerate}
-
-To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
 

### 2024-01-14 paper.tex
Incorporate feedback (#25)
* Added some of the given feedback

* Update paper.tex

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

* deleted subsections

* incorporated review feedback

---------

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 \section{Introduction}
-The development of generative Machine Learning models made huge steps forward in the last years, considering the comparison with human crafted artefacts.
+The development of generative Machine Learning models made huge steps forward in the last years considering the comparison with human crafted artefacts.
 Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles.
-Image generating models like Vision Transformer (ViT) already created fake images being reported as real by media.
+Image generative models like Vision Transformer (ViT) already created fake images being reported as real by media.
 Other news showed artists winning art competitions with generated art.
@@
 Therefore researchers evaluated different approaches to detect fake images and texts.
-Some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e.
-g.
+Some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e.g.
 visual object detection, by artificially manipulating real images.
+
+As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} where the participants try to manipulate a detectable source in a way that the detector does not recognize it as AI-generated anymore.
 This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g.
@@
 
-\subsection{Generating models}
-
-\subsubsection{Image generating models}
-
-\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-They have two primary methods for checking if a text is AI written.
-Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
-One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
-So this method is more generator-specific.
-\cite{WinstonAI}
-
-\subsubsection{Text generating models}
+\subsection{Generative models}
 
@@
 
-\subsubsection{Image detector models}
-
 The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.
 Swin-Transformer by Microsoft is a new Vision Transformer which makes use of hierarchical windows.
-This reduces the self-attention to not-overlapping windows of other areas of the image \cite{liu2021swin}.
+This reduces the self-attention to not-overlapping windows of other areas of the image.
+\cite{liu2021swin}
 
@@
 \cite{he2015deep}
-
-\subsubsection{Text detector models}
 

### 2024-01-14 paper.tex

@@
 
+We used the aforementioned models for generating and detecting texts and images.
+As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise.
+Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera.
+The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}.
+\\
+There are several types of noise that can affect images.
+Some of these noise models are: Gaussian noise, White noise, Fractal noise, Salt \& Pepper noise, Periodic noise, Quantization noise, Speckle noise, Poisson noise, Poisson-Gaussian noise, Structured noise, Gamma noise and Rayleigh noise \cite{gonzalez2009digital}.
+The three common types of image noise are: Gaussian noise, Salt \& Pepper noise, and Speckle noise \cite{al2010comparative}.
+That is why we used those three, as well as the Poisson noise.
+
 \section{Results}

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>

--- 2024-01-14 paper.tex
@@
 \subsubsection{Image generating models}
+The first image generative model we use is the Stable Diffusion model.
+It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
 
-\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-They have two primary methods for checking if a text is AI written.
-Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
-One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
-So this method is more generator-specific.
-\cite{WinstonAI}
+Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
+Due to its work directly in pixel space, they are very computational expensive.
+To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders.
+This works without losing quality and flexibility.
+\cite{Rombach_2022_CVPR}
 

### 2024-01-14 paper.tex
Added citation

@@
 \subsubsection{Image generating models}
-The first image generative model we use is the Stable Diffusion model.
-It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
-
-Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
-Due to its work directly in pixel space, they are very computational expensive.
-To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders.
-This works without losing quality and flexibility.
-\cite{Rombach_2022_CVPR}
 
 \subsubsection{Text generating models}
+We choose the GPT model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
+\begin{enumerate}
+	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
+	\item Discriminative fine-tuning on every specific task.
+\end{enumerate}
+
+To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
 

### 2024-01-14 paper.tex

--- 2024-01-14 paper.tex
@@
 
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
+Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
+One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
+So this method is more generator-specific.
+\cite{WinstonAI}
+
 The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.

### 2024-01-14 paper.tex

@@
 
+We choose the GPT model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
+\begin{enumerate}
+	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
+	\item Discriminative fine-tuning on every specific task.
+\end{enumerate}
+
+To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
+
 \subsection{Detector models}

### 2024-01-14 paper.tex

--- 2024-01-14 paper.tex
@@
 
+As a second image generative model we use Dall-E from OpenaAI (\url{https://openai.com/dall-e-3}).
+Dall-E works by modelling text and image tokens as a single data stream.
+This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+
+This is done in two steps: 
+\begin{enumerate}
+	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
+	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
+\end{enumerate}
+
+The exact procedure proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
+
 \subsection{Detector models}

### 2024-01-14 paper.tex

--- 2024-01-14 paper.tex
@@
 
+The first image generative model we use is the Stable Diffusion model.
+It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
+
+Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
+Due to its work directly in pixel space, they are very computational expensive.
+To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders.
+This works without losing quality and flexibility.
+\cite{Rombach_2022_CVPR}
+
 \subsection{Detector models}

### 2024-01-14 paper.tex
results and discussion part

--- 2024-01-14 paper.tex
@@
 
-We choose the GPT model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
-
-\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
-\begin{enumerate}
-	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
-	\item Discriminative fine-tuning on every specific task.
-\end{enumerate}
-
-To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
-
 \subsection{Detector models}
-
-\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-They have two primary methods for checking if a text is AI written.
-Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
-One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
-So this method is more generator-specific.
-\cite{WinstonAI}
 
@@
 
-\section{Results}
+\section{Results + Discussion}
+In the following we will have a look at the results of the aforementioned experiment.
 
-\section{Discussion}
+In fig.
+\ref{stable_diffusion} can be seen how the different processors and their combinations effect an image generated by the stable diffusion generator.
+The bars are shown in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and lastly on the right is the umm-maybe evaluators respectively.
+The different colors represent different output.
+Black simbolizes that the image before processing was detected as AI-generated and after processing as well.
+Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made.
+Lastly the green bar does exactly what is desired.
+\\
+It can be seen in fig.
+\ref{fig:stable_diffusion}, that only the nahrawy evaluator has a little bit of red in it but also it is the only one with the output of 'human-human'.
+Compared to the dall-E generator in fig.
+\ref{fig:dallE} the amount of green is relatively low.
+There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.
+It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
+This can be seen as they alone achieve a great result as well as their combinations with other ones.
+It is also worth mentioning that these result are only achieved when using the nahrawy evaluator.
+Whereas resnet18 which can be seen in both figures has only the output of 'ai-ai'.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/stable-diffusion.png}
+	\caption{Stable Diffusion with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:stable_diffusion}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/dalle.png}
+	\caption{Dall-E with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:dallE}
+\end{figure}
+
+In fig.
+\ref{fig:gpt2} the text processors can be seen.
+The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
+It is visible that the double-whitespace processor alone has little effect whereas in combination with the typo one the result rise enourmously.
+This is due to the typo processor, since it alone also achieve great results.
+Here is also one evaluator, which produces only a black bar.
+Pretty much the exact same results can be seen in fig.
+\ref{fig:falcon} where radar has just black bars and typo as well as its combination with the roberta base evaluator achieve great results.
+The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/gpt2.png}
+	\caption{GPT2 with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:gpt2}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/falcon.png}
+	\caption{Falcon with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:falcon}
+\end{figure}
+
+All in all can be said that the combination between generators and evaluator plays a huge role in the results.
+In case of the text generators the difference seems minor, but for example just the fact, that the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
+\ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
+This point is even better visible when comparing the figures \ref{fig:stable_diffusion} \ref{fig:dallE} where the importance of the used generators becomes visible.
+The stable-diffusion generator produces images where it is difficult to fool a detector whereas when using the same processors and detectors, the images of dallE can be processed in a way to fool some detectors.
+
+Another importance to notice is the usage of different evaluators.
+In both cases, text and image we had one evaluator respectively which could not be fooled no matter what.
+These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
+If those were the only detectors we would have had, the result would look like there could nothing be done to fool an AI detector.
 

### 2024-01-14 paper.tex
Falcon section

--- 2024-01-14 paper.tex
@@
 
-The first image generative model we use is the Stable Diffusion model.
-It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
-
-Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
-Due to its work directly in pixel space, they are very computational expensive.
-To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders.
-This works without losing quality and flexibility.
-\cite{Rombach_2022_CVPR}
+The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
+Its is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set.
+This data set leverages strict filtering and stringent deduplication to uplift the quality of web data.
+\cite{penedo2023refinedweb}
 

### 2024-01-14 paper.tex
Changed GPT to GPT2

@@
 
-The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
-Its is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set.
-This data set leverages strict filtering and stringent deduplication to uplift the quality of web data.
-\cite{penedo2023refinedweb}
+We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
+\begin{enumerate}
+	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
+	\item Discriminative fine-tuning on every specific task.
+\end{enumerate}
+
+To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
 

### 2024-01-14 paper.tex
added Dall-E version

--- 2024-01-14 paper.tex
@@
 
-The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
-Its is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set.
-This data set leverages strict filtering and stringent deduplication to uplift the quality of web data.
-\cite{penedo2023refinedweb}
+As a second image generative model we use Dall-E 3 from OpenAI (\url{https://openai.com/dall-e-3}).
+Dall-E works by modelling text and image tokens as a single data stream.
+This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+
+This is done in two steps: 
+\begin{enumerate}
+	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
+	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
+\end{enumerate}
+
+The exact procedure proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
 

### 2024-01-14 paper.tex
Fixed Typo
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-14 paper.tex
@@
 
-The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
-Its is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set.
-This data set leverages strict filtering and stringent deduplication to uplift the quality of web data.
-\cite{penedo2023refinedweb}
-
 \subsection{Detector models}
-
-\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-They have two primary methods for checking if a text is AI written.
-Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
-One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
-So this method is more generator-specific.
-\cite{WinstonAI}
 
@@
 
-\section{Results}
+\section{Results + Discussion}
+In the following section we take a look on the results of the aforementioned experiment.
 
-\section{Discussion}
+In fig.
+\ref{stable_diffusion} can be seen how the different processors and their combinations effect an image generated by the stable diffusion generator.
+The bars are shown in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and lastly on the right is the umm-maybe evaluators respectively.
+The different colors represent different output.
+Black simbolizes that the image before processing was detected as AI-generated and after processing as well.
+Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made.
+Lastly the green bar does exactly what is desired.
+\\
+It can be seen in fig.
+\ref{fig:stable_diffusion}, that only the nahrawy evaluator has a little bit of red in it but also it is the only one with the output of 'human-human'.
+Compared to the dall-E generator in fig.
+\ref{fig:dallE} the amount of green is relatively low.
+There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.
+It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
+This can be seen as they alone achieve a great result as well as their combinations with other ones.
+It is also worth mentioning that these result are only achieved when using the nahrawy evaluator.
+Whereas resnet18 which can be seen in both figures has only the output of 'ai-ai'.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/stable-diffusion.png}
+	\caption{Stable Diffusion with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:stable_diffusion}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/dalle.png}
+	\caption{Dall-E with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:dallE}
+\end{figure}
+
+In fig.
+\ref{fig:gpt2} the text processors can be seen.
+The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
+It is visible that the double-whitespace processor alone has little effect whereas in combination with the typo one the result rise enourmously.
+This is due to the typo processor, since it alone also achieve great results.
+Here is also one evaluator, which produces only a black bar.
+Pretty much the exact same results can be seen in fig.
+\ref{fig:falcon} where radar has just black bars and typo as well as its combination with the roberta base evaluator achieve great results.
+The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/gpt2.png}
+	\caption{GPT2 with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:gpt2}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/falcon.png}
+	\caption{Falcon with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:falcon}
+\end{figure}
+
+All in all can be said that the combination between generators and evaluator plays a huge role in the results.
+In case of the text generators the difference seems minor, but for example just the fact, that the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
+\ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
+This point is even better visible when comparing the figures \ref{fig:stable_diffusion} \ref{fig:dallE} where the importance of the used generators becomes visible.
+The stable-diffusion generator produces images where it is difficult to fool a detector whereas when using the same processors and detectors, the images of dallE can be processed in a way to fool some detectors.
+
+Another importance to notice is the usage of different evaluators.
+In both cases, text and image we had one evaluator respectively which could not be fooled no matter what.
+These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
+If those were the only detectors we would have had, the result would look like there could nothing be done to fool an AI detector.
 

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 
-In fig.
-\ref{stable_diffusion} can be seen how the different processors and their combinations effect an image generated by the stable diffusion generator.
-The bars are shown in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and lastly on the right is the umm-maybe evaluators respectively.
-The different colors represent different output.
-Black simbolizes that the image before processing was detected as AI-generated and after processing as well.
+Fig.
+\ref{stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator.
+The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively.
+The different colors represent the different outputs.
+Black symbolizes that the image before and after processing was detected as AI-generated.
 Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made.
-Lastly the green bar does exactly what is desired.
+Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made.
 \\

### 2024-01-14 paper.tex

--- 2024-01-14 paper.tex
@@
 
-As a second image generative model we use Dall-E 3 from OpenAI (\url{https://openai.com/dall-e-3}).
-Dall-E works by modelling text and image tokens as a single data stream.
-This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+The first image generative model we use is the Stable Diffusion model.
+It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
 
-This is done in two steps: 
-\begin{enumerate}
-	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
-	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
-\end{enumerate}
-
-The exact procedure proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
+Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
+Due to its work directly in pixel space, they are very computational expensive.
+To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders.
+This works without losing quality and flexibility.
+\cite{Rombach_2022_CVPR}
 

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-14 paper.tex
@@
 \\
-It can be seen in fig.
-\ref{fig:stable_diffusion}, that only the nahrawy evaluator has a little bit of red in it but also it is the only one with the output of 'human-human'.
-Compared to the dall-E generator in fig.
-\ref{fig:dallE} the amount of green is relatively low.
+The data depicted in fig.
+\ref{fig:stable_diffusion} shows, that only the nahrawy evaluator fooled the detector the wrong way round, but it is also the only one with the output of 'human-human'.
+Compared to the Dall-E generator in fig.
+\ref{fig:dallE} the amount of right tricking is relatively low.
 There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
-This can be seen as they alone achieve a great result as well as their combinations with other ones.
-It is also worth mentioning that these result are only achieved when using the nahrawy evaluator.
-Whereas resnet18 which can be seen in both figures has only the output of 'ai-ai'.
+This can be seen as they solely achieve a great result as well as their combinations with other ones.
+It is also worth mentioning that these results are only achieved when using the nahrawy evaluator.
+Whereas resnet18, which can be seen in both figures, couldn't be tricked by any processor.
 

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 Here is also one evaluator, which produces only a black bar.
-Pretty much the exact same results can be seen in fig.
-\ref{fig:falcon} where radar has just black bars and typo as well as its combination with the roberta base evaluator achieve great results.
+Similar results can be seen in fig.
+\ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results.
 The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.

### 2024-01-14 paper.tex
Mention OpenDalle instead of DALL-E

@@
 
+As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
+OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
+This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+
+This is done in two steps: 
+\begin{enumerate}
+	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
+	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
+\end{enumerate}
+
+The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
+
 \subsection{Detector models}
+
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
+Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
+One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
+So this method is more generator-specific.
+\cite{WinstonAI}
 
@@
 
-\section{Results + Discussion}
-In the following section we take a look on the results of the aforementioned experiment.
+\section{Results}
 
-Fig.
-\ref{stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator.
-The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively.
-The different colors represent the different outputs.
-Black symbolizes that the image before and after processing was detected as AI-generated.
-Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made.
-Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made.
-\\
-The data depicted in fig.
-\ref{fig:stable_diffusion} shows, that only the nahrawy evaluator fooled the detector the wrong way round, but it is also the only one with the output of 'human-human'.
-Compared to the Dall-E generator in fig.
-\ref{fig:dallE} the amount of right tricking is relatively low.
-There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.
-It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
-This can be seen as they solely achieve a great result as well as their combinations with other ones.
-It is also worth mentioning that these results are only achieved when using the nahrawy evaluator.
-Whereas resnet18, which can be seen in both figures, couldn't be tricked by any processor.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/stable-diffusion.png}
-	\caption{Stable Diffusion with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:stable_diffusion}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/dalle.png}
-	\caption{Dall-E with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:dallE}
-\end{figure}
-
-In fig.
-\ref{fig:gpt2} the text processors can be seen.
-The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
-It is visible that the double-whitespace processor alone has little effect whereas in combination with the typo one the result rise enourmously.
-This is due to the typo processor, since it alone also achieve great results.
-Here is also one evaluator, which produces only a black bar.
-Similar results can be seen in fig.
-\ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results.
-The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/gpt2.png}
-	\caption{GPT2 with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:gpt2}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/falcon.png}
-	\caption{Falcon with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:falcon}
-\end{figure}
-
-All in all can be said that the combination between generators and evaluator plays a huge role in the results.
-In case of the text generators the difference seems minor, but for example just the fact, that the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
-\ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
-This point is even better visible when comparing the figures \ref{fig:stable_diffusion} \ref{fig:dallE} where the importance of the used generators becomes visible.
-The stable-diffusion generator produces images where it is difficult to fool a detector whereas when using the same processors and detectors, the images of dallE can be processed in a way to fool some detectors.
-
-Another importance to notice is the usage of different evaluators.
-In both cases, text and image we had one evaluator respectively which could not be fooled no matter what.
-These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
-If those were the only detectors we would have had, the result would look like there could nothing be done to fool an AI detector.
+\section{Discussion}
 

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-14 paper.tex
@@
 
-All in all can be said that the combination between generators and evaluator plays a huge role in the results.
-In case of the text generators the difference seems minor, but for example just the fact, that the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
+To summarize we can say, that the combination between generators and evaluators plays a huge role in the results.
+In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
 \ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 \ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
-This point is even better visible when comparing the figures \ref{fig:stable_diffusion} \ref{fig:dallE} where the importance of the used generators becomes visible.
+This becomes more clear when comparing fig.
+\ref{fig:stable_diffusion} with fig \ref{fig:dallE} where the importance of the used generators becomes visible.
 The stable-diffusion generator produces images where it is difficult to fool a detector whereas when using the same processors and detectors, the images of dallE can be processed in a way to fool some detectors.

### 2024-01-14 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 
-Another importance to notice is the usage of different evaluators.
-In both cases, text and image we had one evaluator respectively which could not be fooled no matter what.
+Another noticeable result is in the usage of different evaluators.
+In both cases, text and image, we had one evaluator respectively which could not be fooled with any method.
 These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.

### 2024-01-14 paper.tex

--- 2024-01-14 paper.tex
@@
 
+The first image generative model we use is the Stable Diffusion model.
+It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
+
+Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
+Due to its work directly in pixel space, they are very computational expensive.
+To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders.
+This works without losing quality and flexibility.
+\cite{Rombach_2022_CVPR}
+
+As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
+OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
+This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+
+This is done in two steps: 
+\begin{enumerate}
+	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
+	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
+\end{enumerate}
+
+The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
+
 \subsection{Detector models}
+
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
+Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
+One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
+So this method is more generator-specific.
+\cite{WinstonAI}
 
@@
 
-\section{Results + Discussion}
-In the following section we take a look on the results of the aforementioned experiment.
+\section{Results}
 
-Fig.
-\ref{stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator.
-The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively.
-The different colors represent the different outputs.
-Black symbolizes that the image before and after processing was detected as AI-generated.
-Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made.
-Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made.
-\\
-The data depicted in fig.
-\ref{fig:stable_diffusion} shows, that only the nahrawy evaluator fooled the detector the wrong way round, but it is also the only one with the output of 'human-human'.
-Compared to the Dall-E generator in fig.
-\ref{fig:dallE} the amount of right tricking is relatively low.
-There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.
-It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
-This can be seen as they solely achieve a great result as well as their combinations with other ones.
-It is also worth mentioning that these results are only achieved when using the nahrawy evaluator.
-Whereas resnet18, which can be seen in both figures, couldn't be tricked by any processor.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/stable-diffusion.png}
-	\caption{Stable Diffusion with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:stable_diffusion}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/dalle.png}
-	\caption{Dall-E with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:dallE}
-\end{figure}
-
-In fig.
-\ref{fig:gpt2} the text processors can be seen.
-The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
-It is visible that the double-whitespace processor alone has little effect whereas in combination with the typo one the result rise enourmously.
-This is due to the typo processor, since it alone also achieve great results.
-Here is also one evaluator, which produces only a black bar.
-Similar results can be seen in fig.
-\ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results.
-The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/gpt2.png}
-	\caption{GPT2 with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:gpt2}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{images/falcon.png}
-	\caption{Falcon with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
-	\label{fig:falcon}
-\end{figure}
-
-To summarize we can say, that the combination between generators and evaluators plays a huge role in the results.
-In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
-\ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
-This becomes more clear when comparing fig.
-\ref{fig:stable_diffusion} with fig \ref{fig:dallE} where the importance of the used generators becomes visible.
-The stable-diffusion generator produces images where it is difficult to fool a detector whereas when using the same processors and detectors, the images of dallE can be processed in a way to fool some detectors.
-
-Another importance to notice is the usage of different evaluators.
-In both cases, text and image we had one evaluator respectively which could not be fooled no matter what.
-These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
-If those were the only detectors we would have had, the result would look like there could nothing be done to fool an AI detector.
+\section{Discussion}
 

### 2024-01-14 paper.tex

@@
 
+We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
+\begin{enumerate}
+	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
+	\item Discriminative fine-tuning on every specific task.
+\end{enumerate}
+
+To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
+
 \subsection{Detector models}

### 2024-01-14 paper.tex

@@
 
+The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
+It is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set.
+This data set leverages strict filtering and stringent deduplication to uplift the quality of web data.
+\cite{penedo2023refinedweb}
+
 \subsection{Detector models}

### 2024-01-14 paper.tex
Apply suggestions from Lukas
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-14 paper.tex
@@
 
-The first image generative model we use is the Stable Diffusion model.
-It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
-
-Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
-Due to its work directly in pixel space, they are very computational expensive.
-To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders.
-This works without losing quality and flexibility.
-\cite{Rombach_2022_CVPR}
-
-As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
-OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
-This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
-
-This is done in two steps: 
-\begin{enumerate}
-	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
-	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
-\end{enumerate}
-
-The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
-
 \subsection{Detector models}
-
-\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-They have two primary methods for checking if a text is AI written.
-Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
-One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
-So this method is more generator-specific.
-\cite{WinstonAI}
 
@@
 
-\section{Results}
+\section{Results + Discussion}
+In the following section we take a look on the results of the aforementioned experiment.
 
-\section{Discussion}
+Fig.
+\ref{stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator.
+The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively.
+The different colors represent the different outputs.
+Black symbolizes that the image before and after processing was detected as AI-generated.
+Grey shows that both are detected to be human made, whereas for red the process did the exact opposite of what it should do and fool the detector in a way that after processing it is seen as AI-generated whereas before as human made.
+Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made.
+\\
+The data depicted in fig.
+\ref{fig:stable_diffusion} shows, that only the nahrawy evaluator fooled the detector the wrong way round, but it is also the only one with the output of 'human-human'.
+Compared to the Dall-E generator in fig.
+\ref{fig:dallE} the amount of right tricking is relatively low.
+There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.
+It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
+This can be seen as they solely achieve a great result as well as their combinations with other ones.
+It is also worth mentioning that these results are only achieved when using the nahrawy evaluator.
+Whereas resnet18, which can be seen in both figures, couldn't be tricked by any processor.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/stable-diffusion.png}
+	\caption{Stable Diffusion with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:stable_diffusion}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/dalle.png}
+	\caption{Dall-E with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:dallE}
+\end{figure}
+
+In fig.
+\ref{fig:gpt2} the text processors are plotted.
+The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
+It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously.
+This is due to the typo processor since it alone also achieves great results.
+The radar evaluator only produces only black bars.
+Similar results can be seen in fig.
+\ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results.
+The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/gpt2.png}
+	\caption{GPT2 with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:gpt2}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{images/falcon.png}
+	\caption{Falcon with different processors and nahrawy, resnet18 and umm-maybe as evaluators}
+	\label{fig:falcon}
+\end{figure}
+
+To summarize we can say, that the combination between generators and evaluators plays a huge role in the results.
+In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
+\ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
+This becomes more clear when comparing fig.
+\ref{fig:stable_diffusion} with fig \ref{fig:dallE} where the importance of the used generators becomes visible.
+The stable-diffusion generator produces images where it is difficult to fool a detector whereas when using the same processors and detectors, the images of dallE can be processed in a way to fool some detectors.
+
+Another noticeable result is in the usage of different evaluators.
+In both cases, text and image, we had one evaluator respectively which could not be fooled with any method.
+These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
 

### 2024-01-14 paper.tex

@@
 
+The first image generative model we use is the Stable Diffusion model.
+It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
+
+Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
+Due to its work directly in pixel space, they are very computational expensive.
+To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders.
+This works without losing quality and flexibility.
+\cite{Rombach_2022_CVPR}
+
+As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
+OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
+This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+
+This is done in two steps: 
+\begin{enumerate}
+	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
+	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
+\end{enumerate}
+
+The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
+
+We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
+\begin{enumerate}
+	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
+	\item Discriminative fine-tuning on every specific task.
+\end{enumerate}
+
+To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
+
+The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
+It is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set.
+This data set leverages strict filtering and stringent deduplication to uplift the quality of web data.
+\cite{penedo2023refinedweb}
+
 \subsection{Detector models}
+
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
+Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
+One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected.
+So this method is more generator-specific.
+\cite{WinstonAI}
 

### 2024-01-15 paper.tex
Changes exclusive for the competition

@@
 \usepackage{iclr2024_conference,times}
+\usepackage{graphicx}
 
@@
 
-\section{Results + Discussion}
+\section{Results \& Discussion}
 In the following section we take a look on the results of the aforementioned experiment.
@@
 Fig.
-\ref{stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator.
+\ref{fig:stable_diffusion} shows how the different processors and their combinations effect an image generated by the stable diffusion generator.
 The bars are structured in packs of three where the most left one represents the nahrawy evaluator, the middle one is resnet18 and on the right is the umm-maybe evaluator respectively.
@@
 
-\section{Conclusion}
+% \section{Conclusion}
 
-\subsubsection*{Acknowledgments}
+% \subsubsection*{Acknowledgments}
 
@@
 
-\appendix
-\section{Appendix}
-You may include other additional sections here.
+% \appendix
+% \section{Appendix}
+% You may include other additional sections here.
 

### 2024-01-17 paper.tex
Add citation and some additional information

--- 2024-01-14 paper.tex
@@
 
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}.
 It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
@@
 It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+The model is limited to English texts only and is openly available under the MIT license.
 

### 2024-01-17 paper.tex
Sort detectors by modality
Extend the method section with text processors

@@
 
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}.
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
 It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
@@
 It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
-The model is limited to English texts only and is openly available under the MIT license.
 
@@
 The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}.
-\\
+
 There are several types of noise that can affect images.
@@
 That is why we used those three, as well as the Poisson noise.
+
+As for text processors, we evaluated on three different methods of augmenting the text.
+The first approach is to replace every white-space in a given text, by two white-spaces.
+The second approach is to add some typos to the texts.
+This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human.
+The typos include mistakes, like not hitting the right key, but a key close to the one, that should have been hit instead.
+This results in typos close to real typos by humans.
+The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english.
+As translator are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
 

### 2024-01-17 paper.tex
minor changes

--- 2024-01-17 paper.tex
@@
 
-The first image generative model we use is the Stable Diffusion model.
+The first image generative model we use is the \textbf{Stable Diffusion} model.
 It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
-
+\\
 Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
@@
 
-As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
+As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
 OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
 This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+\\
+This is done in two steps:
 
-This is done in two steps: 
 \begin{enumerate}
@@
 
-We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning. \\
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
 
-\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
 \begin{enumerate}

### 2024-01-18 paper.tex
Add section about GLTR: Giant Language Model Test Room

--- 2024-01-17 paper.tex
@@
 
+Another tool to automatically detect generated text is \textbf{GLTR}.
+It applies different baseline statistical methods to detect generation artifacts.
+To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated.
+The text is compared with the distribution of next words, in the given context.
+The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context.
+If a text is coloured completely green, a lot of words have a high chance, that they would have been predicted at this position by e.g.
+the currently hosted GPT2 117M model.
+Therefore, it is likely that a mostly green coloured text is generated by the GPT2 model.
+This approach can also be used for other models.
+\cite{gehrmann-etal-2019-gltr}
+
 The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.

### 2024-01-19 paper.tex
Apply rephrasings from Roschtbraten
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-17 paper.tex
@@
 
-As for text processors, we evaluated on three different methods of augmenting the text.
-The first approach is to replace every white-space in a given text, by two white-spaces.
-The second approach is to add some typos to the texts.
+As for text processors, we evaluated three different methods of augmenting generated texts.
+The first approach was to replace every white-space in a given text by two white-spaces.
+The second approach was to add some typos to the texts.
 This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human.
-The typos include mistakes, like not hitting the right key, but a key close to the one, that should have been hit instead.
-This results in typos close to real typos by humans.
+The typos include mistakes, like hitting a wrong key, which is close to the right one.
+This results in typos often created by humans.
 The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english.

### 2024-01-21 paper.tex
Fix typo
Co-authored-by: LeviUniAcc <102458061+LeviUniAcc@users.noreply.github.com>

@@
 The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english.
-As translator are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
+As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
 

### 2024-01-21 paper.tex
Fix typos
Co-authored-by: LeviUniAcc <102458061+LeviUniAcc@users.noreply.github.com>

--- 2024-01-18 paper.tex
@@
 
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
-It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 billion parameters.
 The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
 It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+The model is limited to english texts only and is openly available under the MIT license.
 

### 2024-01-22 paper.tex
Make use of provided command to separate author names

@@
 
-\author{Max Buchholz, Lukas Müller, Levi Otterbach \& Raphael Weber}
+\author{Max Buchholz \And Lukas Müller \And Levi Otterbach \And Raphael Weber}
 
@@
 
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
+The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
+It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+
+The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
+In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
+The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
+
 The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.
@@
 \cite{he2015deep}
-
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}.
-It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 billion parameters.
-The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
-It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
-The model is limited to english texts only and is openly available under the MIT license.
-
-The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
-In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
-The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
 

### 2024-01-22 paper.tex
Add section about grover tool

@@
 
-\author{Max Buchholz \And Lukas Müller \And Levi Otterbach \And Raphael Weber}
+\author{Max Buchholz, Lukas Müller, Levi Otterbach \& Raphael Weber}
 
@@
 This approach can also be used for other models.
-\cite{gehrmann-etal-2019-gltr}
+\cite{gehrmann2019gltr}
+
+A more recent approach is presented in \cite{zellers2020defending}.
+With the aim to investigate in the detection of AI generated fake news,  the authors created a model called \textbf{Grover}, which is on the hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is generated by itself.
+The study also elaborates on how to deal with the issue on generated fake news.
+Therefore, inspired by IT security research, they advocate for the release of such models, to allow the development of effective countermeasures, like detector models.
 

### 2024-01-23 paper.tex
changed to newlines

--- 2024-01-22 paper.tex
@@
 
-The first image generative model we use is the Stable Diffusion model.
+The first image generative model we use is the \textbf{Stable Diffusion} model.
 It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
-
+\newline
 Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
@@
 
-As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
+As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
 OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
 This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+\newline
+This is done in two steps:
 
-This is done in two steps: 
 \begin{enumerate}
@@
 
-We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods.
+The GPT model tries to counter the scarcity of labeled text data for machine learning.
+\newline
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
 
-\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
 \begin{enumerate}
@@
 
-Another tool to automatically detect generated text is \textbf{GLTR}.
-It applies different baseline statistical methods to detect generation artifacts.
-To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated.
-The text is compared with the distribution of next words, in the given context.
-The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context.
-If a text is coloured completely green, a lot of words have a high chance, that they would have been predicted at this position by e.g.
-the currently hosted GPT2 117M model.
-Therefore, it is likely that a mostly green coloured text is generated by the GPT2 model.
-This approach can also be used for other models.
-\cite{gehrmann-etal-2019-gltr}
-
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
-It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
-The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
-It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
-
-The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
-In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
-The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
-
 The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.
@@
 \cite{he2015deep}
+
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
+The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
+It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+
+The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
+In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
+The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
 

### 2024-01-23 paper.tex
back again

@@
 It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
-\newline
+
 Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders.
@@
 This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
-\newline
+
 This is done in two steps:
@@
 
-We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods.
-The GPT model tries to counter the scarcity of labeled text data for machine learning.
-\newline
+We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
+
 \cite{radford2018improving} try to avoid this problem in a simple two step procedure:

### 2024-01-23 paper.tex
Add suggestions
Co-authored-by: RaphaW <116720366+RaphaW@users.noreply.github.com>

--- 2024-01-22 paper.tex
@@
 A more recent approach is presented in \cite{zellers2020defending}.
-With the aim to investigate in the detection of AI generated fake news,  the authors created a model called \textbf{Grover}, which is on the hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is generated by itself.
+With the aim to investigate in the detection of AI generated fake news,  the authors created a model called \textbf{Grover}, which is on the one hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is AI-generated by itself.
 The study also elaborates on how to deal with the issue on generated fake news.

### 2024-01-23 paper.tex
Remove double whitespace
Co-authored-by: LeviUniAcc <102458061+LeviUniAcc@users.noreply.github.com>

--- 2024-01-23 paper.tex
@@
 
+Another tool to automatically detect generated text is \textbf{GLTR}.
+It applies different baseline statistical methods to detect generation artifacts.
+To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated.
+The text is compared with the distribution of next words, in the given context.
+The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context.
+If a text is coloured completely green, a lot of words have a high chance, that they would have been predicted at this position by e.g.
+the currently hosted GPT2 117M model.
+Therefore, it is likely that a mostly green coloured text is generated by the GPT2 model.
+This approach can also be used for other models.
+\cite{gehrmann-etal-2019-gltr}
+
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 billion parameters.
+The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
+It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+The model is limited to english texts only and is openly available under the MIT license.
+
+The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
+In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
+The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
+
 The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.
@@
 \cite{he2015deep}
-
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
-It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
-The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
-It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
-
-The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
-In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
-The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
 

### 2024-01-23 paper.tex
Apply suggestions from code review
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-01-23 paper.tex
@@
 Another tool to automatically detect generated text is \textbf{GLTR}.
-It applies different baseline statistical methods to detect generation artifacts.
+It applies different baseline statistical methods to detect generation artefacts.
 To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated.
-The text is compared with the distribution of next words, in the given context.
+The text is compared with the distribution of possible consecutive words given the semantic context.
 The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context.
@@
 The study also elaborates on how to deal with the issue on generated fake news.
-Therefore, inspired by IT security research, they advocate for the release of such models, to allow the development of effective countermeasures, like detector models.
+Therefore, inspired by IT security research, they advocate for the release of such models to allow the development of effective countermeasures like detector models.
 

### 2024-01-23 paper.tex

--- 2024-01-23 paper.tex
@@
 This approach can also be used for other models.
-\cite{gehrmann-etal-2019-gltr}
+\cite{gehrmann2019gltr}
+
+A more recent approach is presented in \cite{zellers2020defending}.
+With the aim to investigate in the detection of AI generated fake news, the authors created a model called \textbf{Grover}, which is on the one hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is AI-generated by itself.
+The study also elaborates on how to deal with the issue on generated fake news.
+Therefore, inspired by IT security research, they advocate for the release of such models to allow the development of effective countermeasures like detector models.
 

### 2024-01-23 paper.tex
Apply suggestions from Levi
Co-authored-by: LeviUniAcc <102458061+LeviUniAcc@users.noreply.github.com>

--- 2024-01-23 paper.tex
@@
 
-Another tool to automatically detect generated text is \textbf{GLTR}.
-It applies different baseline statistical methods to detect generation artefacts.
-To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated.
-The text is compared with the distribution of possible consecutive words given the semantic context.
-The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context.
-If a text is coloured completely green, a lot of words have a high chance, that they would have been predicted at this position by e.g.
-the currently hosted GPT2 117M model.
-Therefore, it is likely that a mostly green coloured text is generated by the GPT2 model.
-This approach can also be used for other models.
-\cite{gehrmann2019gltr}
-
-A more recent approach is presented in \cite{zellers2020defending}.
-With the aim to investigate in the detection of AI generated fake news, the authors created a model called \textbf{Grover}, which is on the one hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is AI-generated by itself.
-The study also elaborates on how to deal with the issue on generated fake news.
-Therefore, inspired by IT security research, they advocate for the release of such models to allow the development of effective countermeasures like detector models.
-
-The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
-It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
-The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
-It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
-
-The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
-In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
-The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
-
 The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset.
@@
 
+The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2.
+It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters.
+The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model.
+It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.
+
+The \textbf{RADAR-Vicuna-7B} text detector is an adversarial-learning trained model introduced by TrustSafeAI.
+In the training stage a detector tried to differentiate between human and AI text while a paraphraser trained to make the text more human.
+The AI-generated text for learning is extracted by the LLM Vicuna-7B-v1.1 written by LMSYS Org \cite{hu2023radar}.
+
 \section{Method}
@@
 Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera.
-The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}.
-\\
+We used gaussian noice, because it can occure due to natural sources and it is the most common noise that affects images naturally.
+\cite{mohammed2016study}
+
 There are several types of noise that can affect images.
@@
 That is why we used those three, as well as the Poisson noise.
+
+As for text processors, we evaluated three different methods of augmenting generated texts.
+The first approach was to replace every white-space in a given text by two white-spaces.
+The second approach was to add some typos to the texts.
+This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human.
+The typos include mistakes, like hitting a wrong key, which is close to the right one.
+This results in typos often created by humans.
+The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english.
+As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
 

### 2024-01-25 paper.tex
Use correct GPT2 citation
Add section about GPT-4

@@
 To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
+
+A similar model, but in a more recent version is the GPT-4 model.
+The model is yet to be released by it's developer OpenAI, but is available through an API.
+Compared to its predecessors GPT-4 is a multimodal model, which is not only capable of using text for input but also images.
+The model is trained on Next-Token-Prediction and is capable and was post-training aligned to better adhere to desired behaviour.
+The model is capable to perform well in different professional benchmarks out of a variety of domains and can demonstrate it's performance in different languages.
+\cite{openai2023gpt4}
 

### 2024-01-25 paper.tex
Add section about LLAMA 2

@@
 \cite{penedo2023refinedweb}
+
+The \textbf{Llama 2} model built and released by Meta.
+It is available in different sizes, ranging from 7 billion to 70 billion parameters and different appliances like LLAMA 2-Chat, which is optimized for dialogue interaction.
+When it was released in 2023, it outperformed state-of-the-art open source models.
+A main refinement compared to its predecessor LLAMA, was the focus on transparency and safety including a post-training alignment.
+\cite{touvron2023llama}
 

### 2024-01-25 paper.tex
Write section about BLOOM

@@
 \cite{touvron2023llama}
+
+Another generative model for text is \textbf{BLOOM}.
+This huge 176 billion parameter big model was published in 2023 and is openly available.
+The model is multilingual and was built in a decentralized manner by many different contributors.
+Hundreds of researchers helped with the development of the architecture and tokenizer.
+The final model was trained on the Jean Zay supercomputer.
+It is built with a decoder-only architecture and used the ROOTS corpus dataset for training.
+\cite{workshop2023bloom}
 

### 2024-01-27 paper.tex
Added two sections about image detection models

--- 2024-01-25 paper.tex
@@
 
-A similar model, but in a more recent version is the GPT-4 model.
-The model is yet to be released by it's developer OpenAI, but is available through an API.
-Compared to its predecessors GPT-4 is a multimodal model, which is not only capable of using text for input but also images.
-The model is trained on Next-Token-Prediction and is capable and was post-training aligned to better adhere to desired behaviour.
-The model is capable to perform well in different professional benchmarks out of a variety of domains and can demonstrate it's performance in different languages.
-\cite{openai2023gpt4}
-
 The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
@@
 \cite{he2015deep}
+
+Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI.
+The tool first determines different features of the image, e.g.
+colour patterns, shapes and textures.
+These features are determined using machine learning models.
+Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content.
+The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to.
+\cite{IsItAI2024}
+
+There is also an AI-generated-image-detection-approach from Content at Scale.
+They published their \textbf{Advanced AI Image Detector} as a web tool to detect generated AI images.
+The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns.
+\cite{ContentAtScale2024Advanced}
 

### 2024-01-29 paper.tex
Reset citation to iriginal one
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 
-\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
+\cite{radford2019language} try to avoid this problem in a simple two step procedure:
 
@@
 \cite{he2015deep}
-
-Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI.
-The tool first determines different features of the image, e.g.
-colour patterns, shapes and textures.
-These features are determined using machine learning models.
-Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content.
-The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to.
-\cite{IsItAI2024}
-
-There is also an AI-generated-image-detection-approach from Content at Scale.
-They published their \textbf{Advanced AI Image Detector} as a web tool to detect generated AI images.
-The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns.
-\cite{ContentAtScale2024Advanced}
 

### 2024-01-30 paper.tex
add cmd line interface and google collab description

@@
 
-\cite{radford2019language} try to avoid this problem in a simple two step procedure:
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
 
@@
 
+For ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator.
+It is also possible to enter multiple processors for one pipeline that are then stacked and applied together on the images.
+
+The resulting pipelines especially for the images were hardware expensive and could not be runn efficiently on our own machines.
+We chose to use the free google collab recources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time.
+
 \section{Results + Discussion}

### 2024-01-30 paper.tex
Added two more image generative models

--- 2024-01-29 paper.tex
@@
 
+Another image generative model is the \textbf{midjourney} \cite{midjourney}.
+This model was created by an independent research lab with the same name.
+It can synthesize images from textual descriptions.
+Midjourney tends to generate surrealistic images and is popular among artists and it uses modern deep learning methods to create high-quality images.
+
+\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding.
+Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation.
+More information can be found either on their website \cite{imagen} or in their paper \cite{saharia2022photorealistic}.
+
 We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
 
-\cite{radford2019language} try to avoid this problem in a simple two step procedure:
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
 

### 2024-01-30 paper.tex
Added, that they are freely usable through the web

--- 2024-01-29 paper.tex
@@
 \cite{he2015deep}
+
+Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI.
+The tool first determines different features of the image, e.g.
+colour patterns, shapes and textures.
+These features are determined using machine learning models.
+Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content.
+The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to.
+The tool is freely usable through an web interface.
+\cite{IsItAI2024}
+
+There is also an AI-generated-image-detection-approach from Content at Scale.
+They published their \textbf{Advanced AI Image Detector} as a free web tool to detect generated AI images.
+The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns.
+\cite{ContentAtScale2024Advanced}
 

### 2024-01-31 paper.tex
Update midjourney part
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

--- 2024-01-30 paper.tex
@@
 
-Another image generative model is the \textbf{midjourney} \cite{midjourney}.
-This model was created by an independent research lab with the same name.
+Another image generative model is \textbf{midjourney} \cite{midjourney}.
+This model was created by an identically named and independent research lab.
 It can synthesize images from textual descriptions.
-Midjourney tends to generate surrealistic images and is popular among artists and it uses modern deep learning methods to create high-quality images.
+Midjourney tends to generate surrealistic images and is popular among artists.
+It uses modern deep learning methods to create high-quality images.
 

### 2024-02-01 paper.tex
Apply suggestions from code review
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 
-Another image generative model is \textbf{midjourney} \cite{midjourney}.
-This model was created by an identically named and independent research lab.
-It can synthesize images from textual descriptions.
-Midjourney tends to generate surrealistic images and is popular among artists.
-It uses modern deep learning methods to create high-quality images.
-
-\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding.
-Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation.
-More information can be found either on their website \cite{imagen} or in their paper \cite{saharia2022photorealistic}.
-
 We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
@@
 
+For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator.
+It is also possible to enter multiple processors for one pipeline, to stack and apply them together on the content.
+
+The resulting pipelines, especially for the images, were very resource intensive and could not be runned efficiently on our own machines.
+We chose to use the free google collab recources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time.
+
 \section{Results + Discussion}

### 2024-02-05 paper.tex
Extended the image detection part (#50)
* Added two sections about image detection models

* Added, that they are freely usable through the web
Removed Appendix section
First draft of the acknowledgements section

--- 2024-01-30 paper.tex
@@
 \subsubsection*{Acknowledgments}
+We would like to thank the "Gesellschaft für Informatik" for providing the competition "Fool AI Detectors".
+We would also like to thank the teaching assistants of the Foundation Models-Team for their helpful advice.
 

### 2024-02-06 paper.tex

--- 2024-02-05 paper.tex
@@
 
+A similar model, but in a more recent version is the GPT-4 model.
+The model is yet to be released by it's developer OpenAI, but is available through an API.
+Compared to its predecessors GPT-4 is a multimodal model, which is not only capable of using text for input but also images.
+The model is trained on Next-Token-Prediction and is capable and was post-training aligned to better adhere to desired behaviour.
+The model is capable to perform well in different professional benchmarks out of a variety of domains and can demonstrate it's performance in different languages.
+\cite{openai2023gpt4}
+
 The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models.
@@
 \cite{penedo2023refinedweb}
+
+The \textbf{Llama 2} model built and released by Meta.
+It is available in different sizes, ranging from 7 billion to 70 billion parameters and different appliances like LLAMA 2-Chat, which is optimized for dialogue interaction.
+When it was released in 2023, it outperformed state-of-the-art open source models.
+A main refinement compared to its predecessor LLAMA, was the focus on transparency and safety including a post-training alignment.
+\cite{touvron2023llama}
+
+Another generative model for text is \textbf{BLOOM}.
+This huge 176 billion parameter big model was published in 2023 and is openly available.
+The model is multilingual and was built in a decentralized manner by many different contributors.
+Hundreds of researchers helped with the development of the architecture and tokenizer.
+The final model was trained on the Jean Zay supercomputer.
+It is built with a decoder-only architecture and used the ROOTS corpus dataset for training.
+\cite{workshop2023bloom}
 
@@
 \subsubsection*{Acknowledgments}
-We would like to thank the "Gesellschaft für Informatik" for providing the competition "Fool AI Detectors".
-We would also like to thank the teaching assistants of the Foundation Models-Team for their helpful advice.
 

### 2024-02-06 paper.tex
Apply suggestions from Luaks code review
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

@@
 The model is yet to be released by it's developer OpenAI, but is available through an API.
-Compared to its predecessors GPT-4 is a multimodal model, which is not only capable of using text for input but also images.
-The model is trained on Next-Token-Prediction and is capable and was post-training aligned to better adhere to desired behaviour.
-The model is capable to perform well in different professional benchmarks out of a variety of domains and can demonstrate it's performance in different languages.
+Compared to its predecessors, GPT-4 is a multimodal model, which means, that it is not only capable of using texts for input, but also images.
+The model is trained on Next-Token-Prediction and was post-training aligned to better adhere to the desired behaviour.
+The newest GPT-model performs well in different professional benchmarks out of a variety of domains and can demonstrate it's performance in different languages.
 \cite{openai2023gpt4}
@@
 
-The \textbf{Llama 2} model built and released by Meta.
+The \textbf{Llama 2} model was build and released by Meta.
 It is available in different sizes, ranging from 7 billion to 70 billion parameters and different appliances like LLAMA 2-Chat, which is optimized for dialogue interaction.
-When it was released in 2023, it outperformed state-of-the-art open source models.
+When it was released in 2023, it outperformed many state-of-the-art open source models.
 A main refinement compared to its predecessor LLAMA, was the focus on transparency and safety including a post-training alignment.
@@
 
-Another generative model for text is \textbf{BLOOM}.
+Another generative text model is \textbf{BLOOM}.
 This huge 176 billion parameter big model was published in 2023 and is openly available.
@@
 The final model was trained on the Jean Zay supercomputer.
-It is built with a decoder-only architecture and used the ROOTS corpus dataset for training.
+It is build on a decoder-only architecture and uses the ROOTS corpus dataset for training.
 \cite{workshop2023bloom}

### 2024-02-06 paper.tex
Update paper.tex
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

--- 2024-02-06 paper.tex
@@
 
-Another image generative model is \textbf{midjourney} \cite{midjourney}.
-This model was created by an identically named and independent research lab.
-It can synthesize images from textual descriptions.
-Midjourney tends to generate surrealistic images and is popular among artists.
-It uses modern deep learning methods to create high-quality images.
-
-\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding.
-Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation.
-More information can be found either on their website \cite{imagen} or in their paper \cite{saharia2022photorealistic}.
-
 We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
 
-\cite{radford2019language} try to avoid this problem in a simple two step procedure:
+\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
 
@@
 
-Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI.
-The tool first determines different features of the image, e.g.
-colour patterns, shapes and textures.
-These features are determined using machine learning models.
-Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content.
-The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to.
-The tool is freely usable through an web interface.
-\cite{IsItAI2024}
-
-There is also an AI-generated-image-detection-approach from Content at Scale.
-They published their \textbf{Advanced AI Image Detector} as a free web tool to detect generated AI images.
-The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns.
-\cite{ContentAtScale2024Advanced}
-
 \section{Method}
@@
 As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
+
+For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator.
+It is also possible to enter multiple processors for one pipeline, to stack and apply them together on the content.
+
+The resulting pipelines, especially for the images, were very resource intensive and could not be run efficiently on our own machines.
+We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time and allowed to have the same environment for all experiments.
 

### 2024-02-06 paper.tex

--- 2024-02-06 paper.tex
@@
 \cite{penedo2023refinedweb}
-
-The \textbf{Llama 2} model built and released by Meta.
-It is available in different sizes, ranging from 7 billion to 70 billion parameters and different appliances like LLAMA 2-Chat, which is optimized for dialogue interaction.
-When it was released in 2023, it outperformed state-of-the-art open source models.
-A main refinement compared to its predecessor LLAMA, was the focus on transparency and safety including a post-training alignment.
-\cite{touvron2023llama}
-
-Another generative model for text is \textbf{BLOOM}.
-This huge 176 billion parameter big model was published in 2023 and is openly available.
-The model is multilingual and was built in a decentralized manner by many different contributors.
-Hundreds of researchers helped with the development of the architecture and tokenizer.
-The final model was trained on the Jean Zay supercomputer.
-It is built with a decoder-only architecture and used the ROOTS corpus dataset for training.
-\cite{workshop2023bloom}
 
@@
 
-\appendix
-\section{Appendix}
-You may include other additional sections here.
-
 \end{document}

### 2024-02-06 paper.tex
Apply suggestions from code review
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-02-06 paper.tex
@@
 For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator.
-It is also possible to enter multiple processors for one pipeline, to stack and apply them together on the content.
+It is also possible to enter multiple processors for one pipeline to stack and apply them together on the content.
 
-The resulting pipelines, especially for the images, were very resource intensive and could not be run efficiently on our own machines.
-We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time and allowed to have the same environment for all experiments.
+The resulting pipelines, especially for images, were very resource intensive and could not be run efficiently on our own machines.
+We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that speeds up the pipelines up to 40x compared to our local execution time and allowed us to use the same environment for all experiments.
 

### 2024-02-06 paper.tex
Add command line interface and Google Colab description (#52)
* add cmd line interface and google collab description

* Apply suggestions from code review

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

* Update paper.tex

Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

* Apply suggestions from code review

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

---------

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>
Co-authored-by: Max B

--- 2024-02-06 paper.tex
@@
 
+For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator.
+It is also possible to enter multiple processors for one pipeline to stack and apply them together on the content.
+
+The resulting pipelines, especially for images, were very resource intensive and could not be run efficiently on our own machines.
+We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that speeds up the pipelines up to 40x compared to our local execution time and allowed us to use the same environment for all experiments.
+
 \section{Results + Discussion}

### 2024-02-06 paper.tex
Remove sentence

--- 2024-02-06 paper.tex
@@
 
+Another image generative model is \textbf{midjourney} \cite{midjourney}.
+This model was created by an identically named and independent research lab.
+It can synthesize images from textual descriptions.
+Midjourney tends to generate surrealistic images and is popular among artists.
+It uses modern deep learning methods to create high-quality images.
+
+\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding.
+Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation.
+\cite{imagen} \cite{saharia2022photorealistic}.
+
 We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
 
-\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
+\cite{radford2019language} try to avoid this problem in a simple two step procedure:
 
@@
 
+Another AI generated image detector model is \textbf{Is It AI?} developed by Is It AI.
+The tool first determines different features of the image, e.g.
+colour patterns, shapes and textures.
+These features are determined using machine learning models.
+Afterwards, the patterns are compared to those, typically contained in human- or AI-generated content.
+The Is It AI-model was trained on large datasets of human- and AI-generated content to receive the base patterns to compare to.
+The tool is freely usable through an web interface.
+\cite{IsItAI2024}
+
+There is also an AI-generated-image-detection-approach from Content at Scale.
+They published their \textbf{Advanced AI Image Detector} as a free web tool to detect generated AI images.
+The application categorizes the input content by evaluating pixels, smoothness and other AI image patterns.
+\cite{ContentAtScale2024Advanced}
+
 \section{Method}
@@
 As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
-
-For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator.
-It is also possible to enter multiple processors for one pipeline to stack and apply them together on the content.
-
-The resulting pipelines, especially for images, were very resource intensive and could not be run efficiently on our own machines.
-We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that speeds up the pipelines up to 40x compared to our local execution time and allowed us to use the same environment for all experiments.
 

### 2024-02-06 paper.tex
edited citation

--- 2024-02-06 paper.tex
@@
 The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
+
+Another image generative model is \textbf{midjourney} \cite{midjourney}.
+This model was created by an identically named and independent research lab.
+It can synthesize images from textual descriptions.
+Midjourney tends to generate surrealistic images and is popular among artists.
+It uses modern deep learning methods to create high-quality images.
+
+\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding.
+Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation.
+\cite{imagen, saharia2022photorealistic}
 

### 2024-02-06 paper.tex
Repo link
easily REMOVED
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>
started extract

@@
 
-\section{Results + Discussion}
+\section{Results}
 In the following section we take a look on the results of the aforementioned experiment.
@@
 \ref{fig:gpt2} the text processors are plotted.
-The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
+The colors and the concept stay the same, the left bar is using the radar evaluator and the right one the roberta base one.
 It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously.
 This is due to the typo processor since it alone also achieves great results.
-The radar evaluator only produces only black bars.
+The radar evaluator only produces black bars.
 Similar results can be seen in fig.
-\ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results.
+\ref{fig:falcon} where radar and typo just contain black bars, as its combination with the roberta base evaluator achieves great results.
 The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
@@
 
+\section{Discussion}
+
 \section{Conclusion}

### 2024-02-06 paper.tex
Update paper.tex
add initial

--- 2024-02-06 paper.tex
@@
 The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
-
-Another image generative model is \textbf{midjourney} \cite{midjourney}.
-This model was created by an identically named and independent research lab.
-It can synthesize images from textual descriptions.
-Midjourney tends to generate surrealistic images and is popular among artists.
-It uses modern deep learning methods to create high-quality images.
-
-\textbf{Imagen} is a text-to-image diffusion model with an unprecedented degree of photorealism and a deep level of language understanding.
-Imagen builds on the power of large transformer language models in understanding text and hinges on the strength of diffusion models in high-fidelity image generation.
-\cite{imagen, saharia2022photorealistic}
 
@@
 \section{Conclusion}
+Overall we did not find any general fooling technique that can be considered in new AI detectors.
+We discovered that the detector both for the image and text is highly dependent on the used generator and therefore a processor might reduce the detection rate for some detectors, but on others increase the rate.
+Our pipeline consisting of creation, process and detection is simple but effective and can be used in further research.
 

### 2024-02-06 paper.tex
Split up Results and discussion and mention issue with typo processor

--- 2024-02-06 paper.tex
@@
 Lastly the green bar does exactly what is desired, so it pictures AI-generated content, where the executed augmentation lead to the detector guessing it was human-made.
-\\
+
 The data depicted in fig.
@@
 There are also other differences as here only umm-maybe achieved 'human-ai' but also 'human-human'.
-It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
-This can be seen as they solely achieve a great result as well as their combinations with other ones.
-It is also worth mentioning that these results are only achieved when using the nahrawy evaluator.
-Whereas resnet18, which can be seen in both figures, couldn't be tricked by any processor.
 
@@
 \end{figure}
+
+It is visible that the gaussian noise image processor as well as the salt-and-pepper one are the best processors.
+This can be seen as they solely achieve a great result as well as their combinations with other ones.
+It is also worth mentioning that these results are only achieved when using the nahrawy evaluator.
+Whereas resnet18, which can be seen in both figures, couldn't be tricked by any processor.
 
@@
 This is due to the typo processor since it alone also achieves great results.
-The radar evaluator only produces black bars.
+The radar evaluator only results in black bars.
+The results of the translator processor are not shown, as the implementation raised several errors during the experiment, which makes the results not suited for comparison.
+
 Similar results can be seen in fig.
@@
 
-To summarize we can say, that the combination between generators and evaluators plays a huge role in the results.
+\section{Discussion}
+To summarize the results we can say, that the combination between generators and evaluators plays a huge role in the results.
 In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
 \ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
+
 This becomes more clear when comparing fig.
@@
 These evaluators where so strict, that they would even classify a human made image provided by us as AI-generated.
-
-\section{Discussion}
 

### 2024-02-06 paper.tex

--- 2024-02-06 paper.tex
@@
 
-\section{Results}
+The code we used to ran our experiments can be accessed via GitHub: \url{https://github.com/Ctrl-Alt-Defeat-Foundation-Models/informatiCup2024}
+
+\section{Results + Discussion}
 In the following section we take a look on the results of the aforementioned experiment.
@@
 \ref{fig:gpt2} the text processors are plotted.
-The colors and the concept stay the same, the left bar is using the radar evaluator and the right one the roberta base one.
+The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
 It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously.
 This is due to the typo processor since it alone also achieves great results.
-The radar evaluator only produces black bars.
+The radar evaluator only produces only black bars.
 Similar results can be seen in fig.
-\ref{fig:falcon} where radar and typo just contain black bars, as its combination with the roberta base evaluator achieves great results.
+\ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results.
 The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
@@
 
-\section{Discussion}
-
 \section{Conclusion}

### 2024-02-06 paper.tex
abstract draft

@@
 \begin{abstract}
-
+With the current rapid developments in AI generative content, the world gets flooded continuously more with AI generated content and with every new model it gets harder to differ between AI and human generated content.
+This lead to the development of multiple approaches to detect non human-made content like images and texts, e.g.
+to detect fake news.
+This arises the field of tricking AI content detectors to create unrecognized AI generated content to bypass the mentioned AI detectors on the one hand and on the other hand this field is sufficient to improve the existing AI content detectors for more reliability and stability.
+The following paper tries to determine some methods to fool different AI detectors on differently generated images and texts.
 \end{abstract}
@@
 
-The code we used to ran our experiments can be accessed via GitHub: \url{https://github.com/Ctrl-Alt-Defeat-Foundation-Models/informatiCup2024}
-
 \section{Results + Discussion}

### 2024-02-06 paper.tex
Update paper.tex
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-02-06 paper.tex
@@
 \section{Conclusion}
+Overall, we did not find any general fooling technique that can be considered in new AI detectors, but we discovered that the detector, both for the image and text generated content, highly depends on the used generator.
+Therefore a specific processor might reduce the detection rate for some detectors while it increases the detection rate for others.
+Our pipeline consisting of creation, process and detection is simple, but effective, and can be used in further research.
 

### 2024-02-06 paper.tex
changed determine to evaluate
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>
Abstract (#59)
* abstract draft

* changed determine to evaluate

Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

---------

Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>

@@
 \begin{abstract}
-
+With the current rapid developments in AI generative content, the world gets flooded continuously more with AI generated content and with every new model it gets harder to differ between AI and human generated content.
+This lead to the development of multiple approaches to detect non human-made content like images and texts, e.g.
+to detect fake news.
+This arises the field of tricking AI content detectors to create unrecognized AI generated content to bypass the mentioned AI detectors on the one hand and on the other hand this field is sufficient to improve the existing AI content detectors for more reliability and stability.
+The following paper tries to evaluate some methods to fool different AI detectors on differently generated images and texts.
 \end{abstract}

### 2024-02-06 paper.tex
Split up Results and discussion and mention issue with typo processor (#58)
* started extract

* Split up Results and discussion and mention issue with typo processor

---------

Co-authored-by: LukasMueller3 <lukas.mueller@nc-online.de>

@@
 \ref{fig:gpt2} the text processors are plotted.
-The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one.
+The colors and the concept stay the same, the left bar is using the radar evaluator and the right one the roberta base one.
 It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously.
 This is due to the typo processor since it alone also achieves great results.
-The radar evaluator only produces only black bars.
+The radar evaluator only results in black bars.
+The results of the translator processor are not shown, as the implementation raised several errors during the experiment, which makes the results not suited for comparison.
+
 Similar results can be seen in fig.
-\ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results.
+\ref{fig:falcon} where radar and typo just contain black bars, as its combination with the roberta base evaluator achieves great results.
 The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.

### 2024-02-06 paper.tex
Reduce whitespace between figures
Replace enumeration by text

@@
 
-This is done in two steps:
-
-\begin{enumerate}
-	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
-	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
-\end{enumerate}
+This is done in two steps: Firstly, The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
+Secondly, BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
 
@@
 
-We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.
-
-\cite{radford2019language} try to avoid this problem in a simple two step procedure:
-
-\begin{enumerate}
-	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
-	\item Discriminative fine-tuning on every specific task.
-\end{enumerate}
+We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods.
+The GPT model tries to counter the scarcity of labeled text data for machine learning.\cite{radford2019language} try to avoid this problem in a simple two step procedure: Firstly, a generative pre-training of a language model on a varying corpus of unlabeled text.
+Secondly, discriminative fine-tuning on every specific task.
 
@@
 
-\begin{figure}
+\begin{figure}[ht]
 	\centering
@@
 
-Similar results can be seen in fig.
-\ref{fig:falcon} where radar and typo just contain black bars, as its combination with the roberta base evaluator achieves great results.
-The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
-
-\begin{figure}
+\begin{figure}[ht]
 	\centering
@@
 
-\begin{figure}
+Similar results can be seen in fig.
+\ref{fig:falcon} where radar and typo just contain black bars, as its combination with the roberta base evaluator achieves great results.
+The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.
+
+\begin{figure}[ht]
 	\centering

### 2024-02-09 paper.tex
Change heading
Update paper.tex
change some newlines, some wordings and spellings

@@
 \begin{abstract}
-With the current rapid developments in AI generative content, the world gets flooded continuously more with AI generated content and with every new model it gets harder to differ between AI and human generated content.
+With the current rapid developments in AI generative content, the world gets flooded continuously with AI generated content and with every new model it gets harder to differ between AI and human generated content.
 This lead to the development of multiple approaches to detect non human-made content like images and texts, e.g.
@@
 
-As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
+As the second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
 OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
 This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
-
 This is done in two steps: Firstly, The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
 Secondly, BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
-
 The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
@@
 Secondly, discriminative fine-tuning on every specific task.
-
 To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
@@
 
-\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
-They have two primary methods for checking if a text is AI written.
+\textbf{Winston AI} is a commercial AI text detector.
+They describe two primary methods for checking if a text is written by an AI.
 Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
@@
 
-We used the aforementioned models for generating and detecting texts and images.
+We used some of the aforementioned models for generating and detecting texts and images.
+For generating we used Stable Diffusion, OpenDalle, GPT2 and Falcon-RW-1B.
+For detecting we used RoBERTa Base OpenAI Detector, RADAR-Vicuna-7B, AIorNOT and ai-image-det-resnet18.
 As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise.
@@
 This results in typos often created by humans.
-The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english.
+The last approach is a translator, which has been used to translate the given text into a certain language (in this case french) and re-translate it into english.
 As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
@@
 In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
-\ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
+\ref{fig:falcon} before and after process, which means that if that would not have been the case, we would have a perfect score here.
 

### 2024-02-09 paper.tex
restructure discussion

@@
 To summarize the results we can say, that the combination between generators and evaluators plays a huge role in the results.
-In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
-\ref{fig:falcon} before and after process, which means that if that would not have been the case, we would have a perfect score here.
-
-This becomes more clear when comparing fig.
-\ref{fig:stable_diffusion} with fig \ref{fig:dallE} where the importance of the used generators becomes visible.
+This becomes clear when comparing fig.
+\ref{fig:stable_diffusion} with fig \ref{fig:dallE}.
 The stable-diffusion generator produces images where it is difficult to fool a detector whereas when using the same processors and detectors, the images of dallE can be processed in a way to fool some detectors.
+In case of the text generators the difference seems a bit minor but still observable.
 

### 2024-02-09 paper.tex
spelling fix

@@
 This results in typos often created by humans.
-The last approach is a translator, which has been used to translate the given text into a certain language (in this case french) and re-translate it into english.
+The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into English.
 As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.

### 2024-02-09 paper.tex
Change heading
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

--- 2024-02-09 paper.tex
@@
 
-\title{InformatiCup 2024 Ctrl-Alt-Defeat}
+\title{Evaluating the effectiveness of fooling techniques on AI detectors}
 
@@
 \begin{abstract}
-With the current rapid developments in AI generative content, the world gets flooded continuously with AI generated content and with every new model it gets harder to differ between AI and human generated content.
+With the current rapid developments in AI generative content, the world gets flooded continuously more with AI generated content and with every new model it gets harder to differ between AI and human generated content.
 This lead to the development of multiple approaches to detect non human-made content like images and texts, e.g.
@@
 
-As the second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
+As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}).
 OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream.
 This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
+
 This is done in two steps: Firstly, The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
 Secondly, BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
+
 The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}
@@
 Secondly, discriminative fine-tuning on every specific task.
+
 To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
@@
 
-\textbf{Winston AI} is a commercial AI text detector.
-They describe two primary methods for checking if a text is written by an AI.
+\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month.
+They have two primary methods for checking if a text is AI written.
 Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work.
@@
 
-We used some of the aforementioned models for generating and detecting texts and images.
-For generating we used Stable Diffusion, OpenDalle, GPT2 and Falcon-RW-1B.
-For detecting we used RoBERTa Base OpenAI Detector, RADAR-Vicuna-7B, AIorNOT and ai-image-det-resnet18.
+We used the aforementioned models for generating and detecting texts and images.
 As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise.
@@
 This results in typos often created by humans.
-The last approach is a translator, which has been used to translate the given text into a certain language (in this case french) and re-translate it into english.
+The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english.
 As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
@@
 In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig.
-\ref{fig:falcon} before and after process, which means that if that would not have been the case, we would have a perfect score here.
+\ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.
 
